\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=magenta, citecolor=cyan}
\setlength{\parindent}{0in}
\usepackage[margin=1in]{geometry}
\usepackage[english]{babel}
\usepackage{mathtools}
\usepackage{palatino}
\usepackage{fancyhdr}
\usepackage{sectsty}
\usepackage{engord}
\usepackage{parskip}
\usepackage{minted}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{setspace}
%\usepackage[center]{caption}
\usepackage{placeins}
\usepackage{color}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{todonotes}
\usepackage{pdfpages}
% \titlespacing*{\subsection}{0pt}{5.5ex}{3.3ex}
%\titlespacing*{\section}{0pt}{5.5ex}{1ex}
\usepackage{natbib}

\author{Luis Antonio Ortega Andrés\\Antonio Coín Castro}
\date{\today}
\title{Convex optimization \\ \Large Exercises}
\hypersetup{
 pdfauthor={Luis Antonio Ortega Andrés, Antonio Coín Castro},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdflang={Spanish}
 }

\begin{document}

\maketitle


\textbf{Exercise 1. }\emph{Show that if \( S \) is an open set, its complement \( S^c \) is closed, and viceversa.}

\emph{Solution. } Given that \( S \) is open, we got that \( \forall x \in S \ \exists \delta > 0 \ : \ B(x, \delta) \subset S\). By definition \( S^c \subset \bar{S^c}\), where
\[
     \bar{S^c} =  \{x \ : \ \forall \delta\  B(x, \delta) \cap S^c \neq \emptyset \}.
\]
Let \( x \in \bar{S^c} \), then \( \forall \delta > 0 \),
\[
     B(x, \delta) \cap S^c \neq \emptyset \implies B(x, \delta) \not \subset S \implies x \notin S \implies x \in S^c.
\] 
Therefore, we have shown that \( \bar{S^c} \subset S^c \implies \bar{S^c} = S^c\).\\

\textbf{Exercise 2. }\emph{If \( S_1, s_2 \) are convex subsets, prove that \( S_1 \cup S_2, S_1 + S_2 \) and \( S_1 - S_2 \)  are also convex sets.}

\emph{Solution. } Let us begin with \( S_1 \cup S_2 \), let \( x, x' \in S_1 \cup S_2 \) and \( \lambda \in (0,1) \). We got that
\[
     x, x' \in S_1 \cup S_2 \implies  \lambda x + (1-\lambda)x' \in S_1 \text{ and } \lambda x + (1-\lambda)x' \in S_2
\] 
Therefore, \(  \lambda x + (1-\lambda)x' \in S_1 \cup S_2 \), meaning the set is convex. 

Consider now \( x, x' \in S_1 + S_2 \), we can decompose them as \(x = x_1 + x_2 \) and \( x' = x_1' + x_2' \), such that
\[
     \lambda x + (1-\lambda)x' = \lambda x_1 + (1-\lambda x_2) + \lambda x_1' + (1-\lambda x_2') \in S_1 + S_2.
\]

Lastly, consider the set \( S_1 - S_2 \), using the same reasoning used in the previous set, it is convex.\\

\textbf{Exercise 3. }\emph{If \( f: S \to \mathbb{R} \) is a convex function on the convex set \( S \), the set \( \{x : \ x \text{ is a minimum of f} \} \) is a convex set.}

\emph{Solution. } Let \( A = \{x \in S: \ x \text{ is a minimum of f} \} \) and consider \( x, x' \in A \), \( \lambda \in (0,1) \), since \( f \) is convex, there is only one minimal value, ie, \( f(x) = f(x') = c \). Using this, \( x\in A \iff f(x) = c \) and \( \not\exists x \in S \) such that \( f(x) < c \). Therefore
\[
    f(\lambda x + (1-\lambda)x') \leq \lambda f(x) + (1-\lambda)f(x') = f(x) \implies \lambda x + (1-\lambda)x' \in A.
\]
As a result \( A \) is a convex subset of \( S \).\\

\textbf{Exercise 4. }\emph{Let \( f : S \subset \mathbb{R}^d  \to \mathbb{R}\) be a convex function on the convex set \( S \) and we extend it to an \( \hat{f}:\mathbb{R}^d \to \mathbb{R}\) as  }
\[
    \bar{f}(x) = \begin{cases}
        f(x) &\text{ if } x \in S,\\
        +\infty &\text{ if } x \notin S
    \end{cases}
\]
\emph{Show that \( \hat{f} \) is a convex function on \( \mathbb{R}^D \) }.

\emph{Solution}: Let \( x, x' \in \mathbb{R}^d \) and \( \lambda \in (0,1) \),
\begin{itemize}
    \item If \( x,x' \in S \), \( \hat{f}(\lambda x + (1-\lambda)x') \leq \lambda\hat{f}(x) + (1-\lambda)\hat{f}(x') = f(x) \).
    \item If \( x \notin S \), \( \lambda \hat{f}(x) + (1-\lambda)\hat{f}(x) =+\infty \) and the save happens for \( x' \notin S \).    
\end{itemize}

\textbf{Exercise 5. }\emph{If \( Q \) is a symmetric, positive definite \( d \times d \) matrix, show that \( f(x) = x^TQx, \ x \in \mathbb{R}^d \), is a convex function.}\\

\emph{Solution. } We know that \( f \) is convex given that its Hessian its semi-definite positive
\[
    \nabla^2 f(x) = 2Q \geq 0.
\]


\end{document}